Whittaker Models for Real Groups

### 2024-05-01 whittaker.tex
Tiny changes and added todos

In the case of real groups there are other invariants attached to an
irreducible representation $\pi$.  We will be concerned with two of
them, defined very differently. The first is the \emph{wavefront set} $\WF(\pi)$
which is an analytic invariant.
The second is the \emph{associated variety} $\AV(\pi)$, which is
defined  algebraically.
Both consist of nilpotent elements of the dual of the Lie algebra of~$G$, and are defined as
coadjoint orbits (of two different kinds).
The invariants $\Wh(\pi), \WF(\pi)$ and $\AV(\pi)$ are closely related to each other.

@@

\subsection{Some notation}

@@

Let $\N$ be the set of nilpotent elements of $\g$.
This is the closure of the principal nilpotent orbit $\Op$.

@@

@@

We recall some results from,  \cite{vogan_bowdoin}, in particular Corollary 4.7 and Theorem 8.4.

Suppose $\pi$ is an irreducible $(\g,K)$-module.
Let $I_\pi$ be the annihlator of $\pi$ in the universal enveloping algebra.
Let $\AVann(\pi)$ be the associated variety of $I_\pi$.
This is the closure of a single complex nilpotent orbit $\O$.
The associated variety of $\pi$, denoted $\AV(\pi)$, is a closed, $K$-invariant set in $\s$, so it is a finite union of
nilpotent $K$-orbits on $\s$.

@@

Part~(b) is one of the main results of~\cite{vogan_bowdoin}: see \cite[Theorem ?]{vogan_bowdoin}.\footnote{AA 19-II-2024: I'd welcome some help in navigating~\cite{vogan_bowdoin}: the relevant places seem to be  Sections 4, 5 and 8, but I have a few questions.}

Part~(c) follows from~\cite{rossmann_limit_orbits}.\footnote{AA 14-II-2024: maybe a little more detail would be welcome, the Rossmann paper does not seem to state the result in these terms.}
\end{proof}

@@

\end{enumerate}
\end{lemma}
See \cite{vogan_bowdoin}.

@@

\begin{lemma}\label{lem:action_q}
Suppose $\pi$ is an irreducible  Hilbert space representation of $G(\R)$.
Suppose $g\in Q_\sigma(G)$. 
Then $(\pi^g)_K\simeq (\pi_K)^{\phi(g)}$.
\end{lemma}

\begin{proof}
straightforward
\end{proof}

>>>>

There are other invariants attached to an
irreducible representation $\pi$.  We will be concerned with two of
them, defined very differently. The first is the \emph{wavefront set} $\WF(\pi)$
which is an analytic invariant.
The second is the \emph{associated variety} $\AV(\pi)$, which is
defined  algebraically.
Both consist of nilpotent elements of the dual of the Lie algebra of~$G$, and are defined as
coadjoint orbits (of two different kinds).
The invariants $\Wh(\pi), \WF(\pi)$ and $\AV(\pi)$ are closely related to each other.

@@

\subsection{Basic notation}

@@

Let $\N$ be the set of nilpotent elements of $\g$.
This is the closure of the principal nilpotent orbit $\Op$.\footnote{(AA 2024-V-1) Todo: give nice references...}

@@

\footnote{(AA 2024-V-1) Todo: add notation $\pi_K$ and quickly discuss notions of equivalence?}

@@

Suppose $\pi$ is an irreducible $(\g,K)$-module.
Let $I_\pi$ be the annihlator of $\pi$ in the universal enveloping algebra.
Let $\AVann(\pi)$ be the associated variety of $I_\pi$.
This is the closure of a single complex nilpotent orbit $\O$.
The associated variety of $\pi$, denoted $\AV(\pi)$, is a closed, $K$-invariant set in $\s$, so it is a finite union of
nilpotent $K$-orbits on $\s$.\footnote{(AA 2024-V-1) Todo: give nice references, Vogan's Bowdoin paper and others...}.

@@

Part~(b) is one of the main results of~\cite{vogan_bowdoin}: see \cite[Theorem ?]{vogan_bowdoin}.

Part~(c) follows from~\cite{rossmann_limit_orbits}. (Where?)

\footnote{\textcolor{red}{(AA, 2024-V-1) : TODO -- find the right references, I tried but quickly got lost...}}

\end{proof}

@@

\end{enumerate}
\end{lemma}
See \cite{vogan_bowdoin}, in particular Corollary 4.7 and Theorem 8.4.

@@

\begin{lemma}\label{lem:action_q}
Suppose $\pi$ is the equivalence class of an irreducible Hilbert space representation of $G(\R)$. 
Suppose $q\in Q_\sigma(G)$. 
Then $(\pi^q)_K\simeq (\pi_K)^{\phi(g)}$.
\end{lemma}

\begin{proof}
Immediate from Lemma~\ref{lem:iso_q} and the definition of the actions.
\end{proof}
